---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# BetaVolume

<!-- badges: start -->

<!-- badges: end -->

The goal of BetaVolume is to ...

## Installation

You can install the development version of BetaVolume from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("clsong/betavolume")
```

## Example

Here we show a basic example of this package. 
```{r package}
library(BetaVolume)
library(tidyverse)
```

We analyze an empirical metacommunity collected collected by A. H. Gentry and numerous additional collectors. This metacommunity has 81 species and 10 patches.

```{r data_glance}
head(example_meta_composition)
```

As this data only contains information of presence/absence of species, we adopt the duplication schemes to compute hypervolume beta diversity. The hypervolume beta diversity of this metacommunity is
```{r warning=F}
betavolume(example_meta_composition, weights = T)
```

We can disentagle the individual contribution of a patch to the overall beta diversity. We find that 
```{r warning=F}
disentangle_individual_contribution(example_meta_composition, weights = T) %>% 
  enframe(name = "species", value = 'contribution') %>% 
  arrange(-contribution)
```
